Testing Charts: viewers' perceptual accuracy in surveys

### 2023-07-31 SDSS-2023/testing-charts-accuracy.tex
remove 'and'
table 4

\title{Testing Charts: viewers' perceptual accuracy in surveys}
\author{}
\date{}

\begin{document}
\maketitle
\begin{abstract}
The use of visuals is a key component in scientific communication.
Decisions about the design of a data visualization should be informed by
what design elements best support the audience's ability to perceive and
understand the components of the data visualization. We build on the
foundations of Cleveland and McGill's work in graphical perception,
employing a large, nationally-representative, probability-based panel of
survey respondents to test perception in statistical charts. Our
findings provide actionable guidance for data visualization
practitioners to employ in their work.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\caption*{
{\large Estimates for logistic regression on zooming behavior}
} \\ 
\toprule
term & estimate & SE & t-statistic & p-value \\ 
\midrule
\multicolumn{5}{l}{} \\ 
\midrule
\$\$\textbackslash{}hat\{\textbackslash{}mu\}\$\$ & $-0.35$ & $0.15$ & $-2.4$ & 0.0155 \\ 
\midrule
\multicolumn{5}{l}{Response} \\ 
\midrule
\$\$\textbackslash{}text\{They are the same \} \textbackslash{}widehat\{\textbackslash{}rho\}\_\{2\}\$\$ & $-0.17$ & $0.09$ & $-1.9$ & 0.0578 \\ 
Wrong \$\$\textbackslash{}widehat\{\textbackslash{}rho\}\_\{3\}\$\$ & $-0.06$ & $0.13$ & $-0.5$ & 0.6466 \\ 
\midrule
\multicolumn{5}{l}{Task} \\ 
\midrule
Aligned \$\$\textbackslash{}widehat\{\textbackslash{}tau\}\_\{2\}\$\$ & $0.00$ & $0.06$ & $-0.1$ & 0.9435 \\ 
\midrule
\multicolumn{5}{l}{Chart design} \\ 
\midrule
Horizontal wide \$\$\textbackslash{}widehat\{\textbackslash{}delta\}\_\{2\}\$\$ & $0.27$ & $0.15$ & $1.8$ & 0.0752 \\ 
Vertical \$\$\textbackslash{}widehat\{\textbackslash{}delta\}\_\{3\}\$\$ & $0.98$ & $0.13$ & $7.7$ & < 0.0001 \\ 
\bottomrule
\end{longtable}

@@

>>>>

\title{Testing Charts: viewers' perceptual accuracy in surveys}
\date{}

\begin{document}
\maketitle
\begin{abstract}
The use of visuals is a key component in scientific communication.
Decisions about the design of a data visualization should be informed by
what design elements best support the audience's ability to perceive and
understand the components of the data visualization. We build on the
foundations of Cleveland and McGill's work in graphical perception,
employing a large, nationally-representative, probability-based panel of
survey respondents to test perception in statistical charts. Our
findings provide actionable guidance for data visualization
practitioners to employ in their work.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\caption*{
{\large Estimates for logistic regression on zooming behavior}
} \\ 
\toprule
term & estimate & SE & t-statistic & p-value \\ 
\midrule
$\hat{\mu}$ & $-0.35$ & $0.15$ & $-2.4$ & 0.0155 \\ 
\midrule
\multicolumn{5}{l}{Response} \\ 
\midrule
They are the same, $\widehat{\rho_2}$ & $-0.17$ & $0.09$ & $-1.9$ & 0.0578 \\ 
Wrong, $\widehat{\rho_3}$ & $-0.06$ & $0.13$ & $-0.5$ & 0.6466 \\ 
\midrule
\multicolumn{5}{l}{Task} \\ 
\midrule
Aligned, $\widehat{\tau_2}$ & $0.00$ & $0.06$ & $-0.1$ & 0.9435 \\ 
\midrule
\multicolumn{5}{l}{Chart design} \\ 
\midrule
Horizontal wide, $\widehat{\delta_2}$ & $0.27$ & $0.15$ & $1.8$ & 0.0752 \\ 
Vertical, $\widehat{\delta_3}$ & $0.98$ & $0.13$ & $7.7$ & < 0.0001 \\ 
\bottomrule
\end{longtable}

@@

\begin{verbatim}
Warning in RET$pfunction("adjusted", ...): Completion with error > abseps
\end{verbatim}
